### 2008-03-21 trunk/Papers/dl-gre-08/discussion.tex

\subsection{Evaluation: Output Quality}

@@

\newcite{viethen06:_algor_for_gener_refer_expres} describe the data in
more detail and present results of evaluating the Full Brevity
algorithm, the Incremental Algorithm (both by \newcite{Dale1995}), and
the relational algorithm \cite{dale91:_gener_refer_expres_invol_relat}
on this corpus.  Because all these algorithms are sensitive to a
predefined ordering in which predicates and relations are added to the
descriptions, their evaluation methodology is to try all possible
orderings and evaluate what percentage of descriptions an algorithm
can generate with any ordering.  It turned out that the Incremental
Algorithm is capable of generating 98 of the 103 non-relational
descriptions (using four different orderings to cover all the data).
However, the Dale and Haddock algorithm was unable to generate even a
single one of the human-generated relational descriptions.

@@

We replicated Viethen and Dale's experiment for the \el\ algorithm
presented above.  In the non-relational case, our algorithm generates
exactly the same 98 correct descriptions as the Incremental Algorithm;
this is because it performs essentially the same computation if there
are no relations.  To evaluate the relational case, we first removed
the $\mathsf{column}$ and $\mathsf{row}$ predicates from the domain,
because these predicates make it possible to refer to each drawer with
non-relational descriptions, and our algorithm would always prefer
these.  Using three (of 240) different orderings, our algorithm was
able to generate 10 of the 15 human-produced relational descriptions
correctly.  This is shown in more detail in
Fig.~\ref{fig:example_outputs}; notice that four of the 15
descriptions occurred twice in the corpus.  Of the five human-produced
escriptions that the \el\ algorithm cannot generate, two mention
column information, which we excluded from our domain, and three
involve references to sets (\textit{the two blues ones in horizontal
  sequence}/\textit{the two yellow drawers}). While our algorithm
cannot reproduce those descriptions, it does generate other, simpler
descriptions for them.

\subsection{Evaluation: Efficiency}

Both the \el\ and the \alc\ algorithms took about 15 milliseconds to
compute distinguishing concepts for all 16 individuals in the Viethen
\& Dale dataset.\footnote{We measured all runtimes on a MacBook Pro
  (Intel Core 2 Duo, 2.16 GHz) running Java 1.6 beta, and allowed the
  Java VM to warm up, i.e.\ just-in-time compile all bytecode, before
  taking the measurements.}

@@

Our GRE algorithms do not guarantee that the concepts they compute can
actually be realized in language.  For example, none of the concepts
our algorithms computed in the Viethen \& Dale domain contained an
atom that would commonly be realized as a noun; the property
$\mathsf{drawer}$ is never used because it applies to all individuals
in the domain.  This particular problem could easily be worked around
in a post-processing step.  However, another problem arises from the
massive use of negation in the \alc\ algorithm; it will be hard for
any realizer to find a reasonable way of expressing a concept like
$\neg \exists R.(\neg P \sqcap \neg Q)$ as a smooth noun phrase.
Although we agree with \newcite{deemter01:_gener_refer_expres} and
others that the careful use of negation and disjunction can improve
REs, these connectives must not be overused.  Thus we consider the
concepts computed by the \el\ algorithm ``safer'' with respect to
realization.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{runtimes}
  \caption{Average runtimes (in ms) of the two algorithms on random
    models of     different sizes.} 
  \label{fig:runtimes}
\end{figure}

>>>>

\subsection{Evaluation: output quality}

@@

\newcite{viethen06:_algor_for_gener_refer_expres} describe the data in
more detail and present results of evaluating the Full Brevity
algorithm, the Incremental Algorithm (both by \newcite{Dale1995}), and
the relational algorithm \cite{dale91:_gener_refer_expres_invol_relat}
on this corpus. The Incremental Algorithm is dependent on a predefined
ordering in which properties are added to the description. Viethen and
Dale, therefore, try all possible orderings and evaluate what
percentage of descriptions an algorithm can generate with any of
them. The Full Brevity and the Relational Algorithms choose properties
based on their disciminatory power and only use the orderings as tie
breakers. Viethen and Dale found that the Incremental Algorithm is
capable of generating 98 of the 103 non-relational
descriptions. However, the Dale and Haddock algorithm was unable to
generate even a single one of the human-generated relational
descriptions.

%(using four different orderings to cover all the data).

@@

We replicated Viethen and Dale's experiment for the \el\ algorithm
presented above. In the non-relational case, our results are the same
as their's for the Incremental Algorithm: the \el\ algorithm generates
98 of the 103 non-relational description; this is because the two
algorithms perform essentially the same computations if there are no
relations.

To evaluate the relational case, we first removed the
$\mathsf{column}$ and $\mathsf{row}$ predicates from the domain,
because these predicates make it possible to uniquely identify each
drawer with non-relational descriptions, and our algorithm would
always prefer these.  Using three (of 240) different orderings, our
algorithm was able to generate 10 of the 15 human-produced relational
descriptions correctly.  This is shown in more detail in
Fig.~\ref{fig:example_outputs}; notice that four of the 15
descriptions occurred twice in the corpus.  Of the five human-produced
descriptions that the \el\ algorithm cannot generate, two mention
column information, which we excluded from our domain, and three
involve references to sets (\textit{the two blues ones in horizontal
sequence}/\textit{the two yellow drawers}). While our algorithm cannot
reproduce those descriptions, it does generate other, simpler
descriptions for them.

\subsection{Evaluation: efficiency}

Both the \el\ and the \alc\ algorithms took about 15 milliseconds to
compute distinguishing concepts for all 16 individuals in the Viethen
and Dale dataset.\footnote{We measured all runtimes on a MacBook Pro
  (Intel Core 2 Duo, 2.16 GHz) running Java 1.6 beta, and allowed the
  Java VM to warm up, i.e.\ just-in-time compile all bytecode, before
  taking the measurements.}

@@

Our GRE algorithms do not guarantee that the concepts they compute can
actually be realized in language.  For example, none of the concepts
our algorithms computed in the Viethen and Dale domain contained an
atom that would commonly be realized as a noun; the property
$\mathsf{drawer}$ is never used because it applies to all individuals
in the domain.  This particular problem could easily be worked around
in a post-processing step.  However, another problem arises from the
massive use of negation in the \alc\ algorithm; it will be hard for
any realizer to find a reasonable way of expressing a concept like
$\neg \exists R.(\neg P \sqcap \neg Q)$ as a smooth noun phrase.
Although we agree with \newcite{deemter01:_gener_refer_expres} and
others that the careful use of negation and disjunction can improve
REs, these connectives must not be overused.  Thus we consider the
concepts computed by the \el\ algorithm ``safer'' with respect to
realization.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{runtimes}
  \caption{Average runtimes (in ms) of the two algorithms on random
    models with different numbers of individuals.}%%of different sizes.} 
  \label{fig:runtimes}
\end{figure}
